### 2021-09-23 varia/NEE/Response_to_reviewers.Rmd

Also, based on the title and abstract of this paper, I expected a discussion of how fish community structure as a whole, and not just species diversity, need to be explicitly considered when estimating how fish affect functioning in coral reefs. There are a couple of places where this topic is briefly touched upon, but this should be directly addressed in both the introduction and discussion. This would also allow the authors to discuss a key finding, that biomass is the key predictor for ecosystem functioning across reefs. I know that, and agree with, the biomass-corrected variables used in the paper. But I don’t see why the authors couldn’t use and discuss both biomass effects, and then biomass independent effects. That seems like a huge part of this story, and that there actually IS a global pattern in how fish communities affect ecosystem functions in reefs. The authors mention that their work reveals that there is no clear objective for protecting coral reef functioning, and there are no global keystone species to target. It is unclear how exactly the authors evaluated those statements, and is surprising that the authors have no recommendations that would help address those clear conservation goals from their global analyses.
*We now mention the role of community structure in the introduction. In the discussion, we both discuss the effect of biomass and community structure as a whole. We also modified the discussion on conservation. We now say: "It is necessary to gauge the state of reef ecosystems based on multiple, complementary, process-based functions, yet our comprehension of
process-based functioning of coral reefs or what a “functional” coral reef really means is still in its infancy.
To appropriately manage coral reef functioning with respect to local needs and stressors, future studies should seek to establish functional baselines for global coral reefs.
Until then, our study suggests that coral reef fish functions can be managed by enhancing standing stock biomass, protecting local key species, and promoting a balanced community structure."*

---
Section/Line comments
Abstract:
This section is very strong. The authors should use the focus of each of these sentences to guide the topic sentences of the manuscript sections. Clear and concise!
*Thank you. We aimed to clarify all topical sentences.*

Introduction:
The introduction could use a rewrite with clarity and concision in mind. Between lines 25-42, I counted way too many uses of words and phrases that contradict the statement made before (e.g., “However, ….” , “…but simultaneously quantifying”, “Yet, the integrity of reefs” etc.). This is indicative of an unfocused introduction. The central message is simple enough that the authors should be more specific and precise with their wording and sentences.
*We rewrote the introduction and avoided using many contradicting words. We believe the introduction is now more focused.*

3- “integrity” of ecosystems is vague, especially when the authors actually mean “functioning.” Could actually just remove this opener and start with the next sentence, which is pretty good. In that sentence, and throughout, be careful with informal language. “The world’s coral reefs” can be replaced with “Coral reefs” (I don’t think any readers are going to be thinking of any coral reefs on other worlds!) and “today’s coral reef conservation efforts” to “current coral reef conservation efforts”.
*We removed the word 'integrity' throughout the manuscript. We also avoided using informal language and removed the given examples.*

21- “integrity” repeated here again. Still unsure what the integrity of an ecosystem means.
*Agreed, it is a rather confusing and vague term. We removed it.*

22- careful with switching tenses here. This sentence could probably be removed.
*Done.*

23-25 why does sustaining multiple functions require both high richness and a variety of species assemblages? Also, what does “a variety of species assemblages” mean? Are the authors trying to say that community structure as a whole, and not just biodiversity, is key to a multifunctional ecosystem? If so, that is a fantastic point to make and represents a huge gap in ecology today!
*This section has been changed entirely.*

31-42 I was surprised that this paragraph doesn’t fully focus on the role of fishes in nutrient cycling/ecosystem functioning in coral reefs.
*The second paragraph of the introduction now focuses on fishes.*

33- “integrity” repeated again. Do you mean function?
*No more integrity in this manuscript.*

34- An example of an edit to be more concise: the authors wrote “a plethora of stressors” and then added “such as….”. Pick one of the two of these. I would suggest getting rid of “a plethora of”.
*Done as suggested.*

37 Generally it is better to write out exactly why a topic is “at the forefront of scientific discourse” as opposed to just stating that it is. Because the reader is left to ask, why?
*We removed this sentence and now say: "Drastic declines in habitat quality and fish biomass have evoked serious concerns about the persistence of coral reef functioning."*

40-2 These two sentences are a good example of where this introduction goes astray. First, the sentence starts with “Conversely, …” but the sentence does not offer information that is counter to the previous sentence (not to mention that the previous sentence began with an “However” further obscuring the main point. I suppose “additionally” would be more appropriate, but it’s still unclear. I’m not sure that it is true that we know little about elemental fluxes and their drivers, as claimed. Are you talking about the role of reef fish in elemental fluxes? Be precise. Next, the Allgeier paper cited here as a “but see” example examines exactly what the authors claim that we know comparatively little about. That citation seems like a very good jumping off point for this paper, considering the differences in scale in this paper (global) vs that one (multi-site). Finally, the ending sentence offers no reasoning. Why does “this” (again even the “this” is
unclear, is it that we have only proxies of functioning, or that we know little about elemental fluxes? Or both?) constitute a severe limitation.
*As mentioned above, we rewrote the introduction entirely, and hope you will find it has improved in clarity.*

Paragraph on line 86 This paragraph talks a lot about “species” roles, but the figure shows taxa groups in families. This gets confusing when claims like “functions consistently hinge [upon] a few dominant species” (line 92-3) are made. Do you mean, “a few dominant families”? Or are there key species that provide high functioning?
*We understand the confusion, and now removed the part of the figure shhowing the contribution of fish families as it was not a main result and distracts the reader from the main point which is indeed that on a local scale a few key species provide high functioning while the identity of these key species vary across sites.*

97-100 These results seem like a very interesting implication of this research, but I don’t know where in the figures the reader can see this. Without a visual, this is difficult to interpret. Determine how important this finding is, and decide how to get this across in a more clear way. Also, please make sure that this isnt directly repetitive from the introduction.
*We now have a seperate results paragraph accompagning figure 4. We hope this clarifies these findings.*

102-105 See below comment on line 122. This reads like a topic sentence. Readers are going to be very interested in the details behind the claim that both species richness and functionally dominant key species are important to maximize the functions provided by reef fish. Regardless, this sentence doesn’t quite mesh with the opening sentence of this paragraph, so please edit for clarity here.
*The topical sentence of this paragraph is now: "Our results also reveal that functions consistently hinge on a few dominant species, but the identities of local, dominant species vary strongly across sites."*

108 I’m not sure what a “severe change” is, especially in a broad term like community structure.
*We modified the sentence as followed: "Fishing and climate-induced coral loss have caused declines in reef fish biomass and shifts in community structure."*

112 “effect” used twice in one sentence.
*Changed to: "When accounting for the effect of biomass, these community shifts can..."*

114 is this what Fig 2 shows? Do you mean Fig 4? Unclear
*We removed the mention of the figure in this discussion paragraph as we now have a seperate results section.*

114-116 “On the other hand” and “However” open back to back sentences. This is a clear indication that whatever points are trying to be made, are unfocused.
*We edited the section and replaced 'on the other hand' to 'further', and 'However' to 'Simultaneously'.*

122 This closing sentence for this paragraph is a great example of something that happens a lot in this paper. The paragraph above it is wavering, with an unclear main theme. This last sentence is actually quite good and brings up a fantasticthough point. It reads much more like a topic sentence. Considering the topic sentence of this paragraph is pretty vague (i.e., “shines new light on” doesn’t tell us anything specific), the authors should consider a reordering of the logic flow here, in above paragraphs, and in the discussion section as a whole.
*The topical sentence of this paragraph now reads: "Our global analysis of multiple functions suggests pathways in which human-induced shifts in reef fish community structure may impact coral reef ecosystems."*

122-4 I’m not sure that something can be both nuanced and holistic. Rephrase.
*We removed the sentence.*

125 “Similarly…” It is unclear what is similar here. Rephrase
*We removed this paragraph as suggested below.*

134 What does this sentence mean? How do herbivores fishes have a high variability in species roles? Should you have grouped the species roles differently then, into categories like “grazers of macroalgae” “bioeroders” “grazers of microalgae”? You defined what an herbivore is, so it’s strange to see that high variability is explained by your too-broad definition of herbivore.
135,137 Back to back sentences beginning with “While”.

137 …But can you not do this, with the data you have collected? The whole end of this paragraph is confusing and needs to be revisited.
*We removed this paragraph altogether.*

@@

Figure Comments:

Fig 1- This figure encapsulates the scale and scope of these analyses in a really nice way. There isnt a lot of specific information that can be gathered from this figure, besides that there were a lot of sites all throughout the world (which is a great thing!). Do the authors want to highlight that there are hotspots of function in different places, for different functions? If so, probably just include the colored points. Also, would there be any value in a figure that shows the highest multifunctional sites, i.e., where multiple processes are occurring at high rates? Identifying the global multifunctional hotspots of coral reef fish communities could be of value to conservation and management.
*We now edited this first figure to show the actual function estimates per location, as well as a measure of multifunctionality.*

Fig 2. In the caption (181), do you mean “effect size” or “average effect size estimate” as opposed to “fixed effect values”? Regardless, the community variables besides richness mapped out in this figure are unclear. What is the difference between the 97.5% size line and the 2.5% size line? Is 97.5% size mean that the fish community is mostly made up of large fish? Maybe come up with more descriptive variable names than this? I definitely do not know what the immaturity variables are supposed to represent, and how they are different to size. This is further unclear when looking back at the ms text in line 78 that implies that small/immature fish are the same.
*This is now figure 3. We modified the x-axis label to "standardized effect size" and the percentages to lower and upper. We provided extra information in the legend. An individual fish can both be small and mature, so both variables are quite different. Immaturity is a measure that represents the position in the growth curve. We now also added a definition in the legend.

Fig 3. The axis on 3a needs to be explained better. Dots to the right of the 0 line indicate that this family contributes more to this function than as predicted by biomass? Actually, all axes need to be explained better
*We removed figure 3a.*

Fig 4. I understand what the authors are trying to do here, but I’m not sure that this figure is necessary. Which functions are vulnerable to climate change and overfishing can be discussed in words without too much confusion. This figure, and the paragraph in the main text surrounding it, seem out of place.
*As suggested, we removed this figure and the paragraph surrounding it. Instead, we now provide a conceptual figure that supports this part of the discussion.*

@@

Methods:
Section 3 Did I miss a mention of the priors used here? I see uninformative priors are used in section 4
80 “fitted” should be “fit” ?

*We added more information on the priors everywhere.*

Supp Methods
A strength of this manuscript is the synthesis of multiple data sources and analytical techniques. However, this creates a lot of methods and thus, requires that even the supplementary methods need to be extra clear. It would be helpful to add a topic sentence to each relevant section of the Supp Methods so that the reader knows why each method is being used and explained. For example, line 3 should say exactly what parameters are going to be explained in this Supp Methods section, instead of “a number of parameters are required.” Carry this clarity throughout this Supp Methods section. For example, start section 1 (or 1.1) with something along the lines of, “To estimate the growth parameters of fish species (or families?) in our database, we used maximum length from fishbase and collected otolith data…”. Without this, it is difficult to tell why techniques like the Bayesian phylogenetic regression model are necessary.
*We now added much more information and introductory sentences in the supplementary methods.*

@@

Reviewer #3 (Remarks to the Author):

Review of Global drivers and vulnerabilities of coral reef fish functions

I enjoyed reading this paper. Using coral reef fishes as a model system, it contains a simple but important message: a given ecosystem function can exist on a coral reef due to a relatively small number of species being present (and the identify of these species contributing to this particular function varies across geographies). The paper also contains an important applied message: that maintaining high levels of species richness across coral reef regions is essential to sustain global ecosystem function on coral reefs. The paper is well written, although I think some statements could be clarified in places (see minor comments below).

*Thank you, we are delighted that you enjoyed reading our paper. We clarified the text as specified below.*

My only major comment is the need to better justify the five key ecosystem functions that you focus on for the reader. I understand these are taken from the Brandl et al. paper, but many readers may not realise. Also, why 5 and not the 8 presented by Brandl et al.? This needs to come early on so the reader feels comfortable with your focused choice – your paper hinges on this to some extent. I suggest building this out in paragraph three (lines 43-53). You can do this in 2-3 strong sentences.
*We substantially modified the introduction and added a paragraph on fish-mediated functions specifically. We agree that quantifying all functions proposed by Brandl et al. would have been even better. However, we did not have access to data to do so. For example, CaCO3 production by corals requires on detailed data on coral cover including the community composition and the sizes of corals. We did not have any data on benthic cover for this specific project. We thus only analyzed the functions that are related to fishes based on the data available and the confidence in methodology.*

@@

Minor comments

Lines13-16. Link between these two sentences is not clear for the reader: “Furthermore, functions are locally dominated by few species, but worldwide, 70% of the 1110 species in our dataset contribute disproportionally to functioning in at least one local community. This leads to disparate vulnerabilities of functions to anthropogenic stressors”
*We removed the second sentence.*

Lines 18-19 – are you suggesting here that conservation strategies to maximize function will always need to be context dependent – I think you are. If so, I would state this more clearly, as this is an important message from the data.
*We now say: "Our results underline the need for a nuanced, local, and context-dependent approach to coral reef conservation that considers multiple functions beyond the effect of standing stock biomass."*

Line 32-33. Not just efficient recycling of nutrients that’s key to their persistence in oligotrophic waters, it’s also about the feedbacks that raise primary production levels around coral reefs (Gove et al. 2016 Nature Comms 7: 10581) and the flexible trophic ecology of corals to exploit these resources (Fox et al. 2018 Current Biology 28: 3355-3363).
*Agreed. However, we now removed this sentence following the suggestion of reviewer 1. MAYBE I SHOULD INCLUDE THIS??*

Line 37. Suggest adding Williams & Graham (2019) Funct Ecol 33: 942-947 to references here also as this editorial captures the messages from a suite of studies talking about functional changes to coral reefs in the Anthropocene.
*Done.*

Line 41 – “but see 18”. Please tell us what Allgeier et al. found – annoying for reader to have to go and read another paper to understand this statement.
*Done. We now state this explicitely.*

Line 41-42. How exactly is this hindering effective management of reefs? You leave the reader guessing here – poor style.
*We now say: "This sparsity of quantification of functions constitutes a severe limitation to efficient management of coral reef ecosystem functioning." I AM NOT SURE THAT THIS SUFFICES. ANY SUGGESTIONS?*

Line 69. Suggest avoid the term “holistic”, nothing can ever truly be holistic, without mentioning the connotations of unscientific holistic medicines.
*We removed the word 'holistic'.*

Line 78. “and/or” is poor style. You can just write “and”. If a mechanic was advertising that their garage fixes exhausts “and” steering systems, you could take your car there to have both fixed, or just one….they are not implying it has to be both at the same time!
*Good point, we changed it to 'and'.*

Line 93. I think this is meant to read “consistently hinge on”.
*Modified as suggestes.*

Line 107. Contributions to what?
*Contributions to functions. We removed this specific sentence though.*

Line 108-109. The Hughes et al. reference is not appropriate here as it does not address “reef fish”.
*Agreed. We removed the reference here.*

Line 119-120. Why does a shift in algal symbiont dominance matter? I think you need to make it clearer to reader here why this (and algal growth) are considered bad (if that is what you are implying).
*We simplified this section and now say: ... so a shift to herbivore dominance and the subsequent decline of community-level P excretion may change the balance of nutrient cycling on coral reefs, potentially favoring algal growth in comparison with corals.*

Line 123. Same comment about use of “holistic”.
*We removed the word holistic.*

Line 125. Poor style to start a new paragraph with “similarly”. Too much connection/reliance on previous sentence that sits in a different paragraph.
*We removed this entire paragraph.*

Line 132-133. Can impact smaller browsers also, see Heenan et al. (2016) Proc B 283: 1843 (Fig. 3).
*Same.*

Line 164. Suggest replace “through” with “using”.
*Done as suggested.*

Figure 1. Why is there no key for the bubble values? The size differences between bubbles is also not that clear – can this be emphasized? Also not clear what the “categorical assignments” are from the figure legend alone – please expand the explanation.
*We added extra details in the legend.*

Figures 2-4. Don’t take this the wrong way, but I find the choice of primary colours in your figures rather off-putting (in particular Fig 4). Also, the choice of some color combinations could be more inclusive (e.g. your use of red/green to denote different groups). There are plenty of color-blind friendly palettes out there now.
*The color palette was created based on the natural colors of a coral reef fish species: Callanthias australis. We regret that the reviewer found the colors off-putting. We tested the color combination by simulating color-blindness using the website https://coolors.co/ and the red green combination seem to be distinguishable due to differences in clarity. Moreover, as functions are kept in the same order throughout the paper, the results could be interpreted even if there were no colors at all. Therefore, we decided to keep the colors for now, but if this is a big issue for the reviewer or the editor agrees with the reviewer, we will change the color palette.*

Figure 2 seems unnecessarily large – this could be a single column figure.
*Agreed. We decreased the size.*

Figure 4 – Suggest proportion values radiating out run to 1 so piscivory falls within the axis bounds.
*This is a great point, thanks for noticing. However, following a recommendation of reviewer 2, we now actually removed this figure.*

All Figures – there are some inconsistencies in font use/size across your figures. This might seem picky, but important for consistency.
*We standardized sizes and fonts as much as possible.*

Did you synthesize this data set yourself or did you use an existing database that has been previously published from? Please make this clear in the main manuscript.
*We used an existing underwater visual census database that has been previously published from. We collected extra data ourselves to parametrize bioenergetic models. We stated this more clearly now.*
